Reliable Inferences from Simply Parameterised Models

### 2012-08-29 ms.tex
More writing on sigma boost etc

\section{The Failure of Simply Parameterised Models}
\begin{itemize}
\item Easy to implement \\
\item Computationally fast to get inferences - therefore can be applied on a large scale, e.g. to large samples of objects. \\
\item Easy to assign non-controversial priors over low dimensional parameter spaces \\
\end{itemize}

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.25]{simple_complex1.eps}
\includegraphics[scale=0.25]{simple_complex2.eps}
\includegraphics[scale=0.25]{simple_complex3.eps}
\end{center}
\end{figure*}

@@

>>>>

\subsection{The Failure of the Simply Parameterised Model}
We ran the simply parameterised model on the simulated data using the Diffusive
Nested Sampling algorithm \citep{dnest}
\footnote{A C++ implementation of Diffusive Nested Sampling is available
online at {\tt http://github.com/eggplantbren/DNest3/}.}. This provides samples
from the posterior distribution for the parameters $A$, $c$ and $w$. Since these
parameters do not ``exist'' in reality (i.e. the data were generated from the
complex model), it does not make much sense to look at the posterior distribution
for the parameters. However, consider the total flux:
\begin{eqnarray}
F = \sum_{i=1}^N \mathcal{M}(x_i)
\end{eqnarray}
This can be computed both for the true underlying complex model, and the fitted
simple models. In other words, it ``exists''. We computed the posterior distribution
for the total flux using the posterior samples. These are plotted in
Figure~\ref{failure}.

A commonly suggested technique \citep[e.g.][]{gregory} to avoid this situation
is to add an ``error-bar boost'' parameter which we will call $\kappa$.
This adds one more parameter to the list, and the likelihood becomes:
\begin{eqnarray}
p(\yy|A, c, w, \kappa) &=& \prod_{i=1}^N
\frac{1}{(\kappa\sigma)\sqrt{2\pi}}
\exp
\left[
-\frac{1}{2(\kappa\sigma)^2}\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2
\right] \\
&\propto& \kappa^{-N}\exp\left[-\frac{1}{2(\kappa\sigma)^2}\sum_{i=1}^N\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2\right]
\end{eqnarray}

\begin{itemize}
\item Easy to implement \\
\item Computationally fast to get inferences - therefore can be applied on a large scale, e.g. to large samples of objects. \\
\item Easy to assign non-controversial priors over low dimensional parameter spaces \\
\end{itemize}

@@

@@

\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay, 
\& Cs{\'a}nyi}{2011}]{dnest} {\bf Brewer B.~J.}, P{\'a}rtay L.~B., Cs{\'a}nyi G., 2011, Diffusive Nested Sampling, 
Statistics and Computing, 21, 4, 649-656.
